We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-05-01 paper/paper.tex
results

In the following subsections we describe in detail the results on the 
distributions for $w$, $c/a$ and $b/a$ and its comparison against
observations. 
The plots in the main body of the paper correspond to the
Illustris-1-Dark simulation and $N_s=11$; the results from the other
two simulations are included in the Appendix \ref{appendix:plots}.

\subsection{Plane Width}

Figure \ref{fig:scatter_width} summarizes the results for the width
measurements.
The left panel compares the results for the MW and M31
observations (stars) against its spherically randomized satellites
(circles). 
The most interesting outcome is that the MW plane width is smaller
than $\approx 98\%$ of the planes computed from the randomized distribution,
while the M31 plane width is only slightly smaller than the average of
the distribution.

@@

The left panel in Figure \ref{fig:scatter_ca_ratio} shows how the MW
$c/a$ ratio is significantly lower than the measured values for
spherical distributions, and it is smaller than $\approx 98\%$ of the
randomized distributions.   
On the other hand the ratio for M31 is lower than the mean of the
spherical values but still well within its variance.
The middle panel in the same Figure shows the LG compared against the
results in the simulations. 
In this case we find a similar trend as before. 
The MW is atypical and M31 is within the variance from the simulation data.
This time, however, there are two MW-like halos out of the total
of 24 that show an $c/a$ as small as that of the MW.
The right panel shows the normalized results. 
The MW shows a low $c/a$ ratio between two and three
standard deviations away from the mean value of the spherical
distribution; this contrasts with the results for M31 which are close to
$1$ standard deviation away.

@@

\subsection{Fit to a Multivariate Gaussian Distributions}

>>>>

In the following subsections we describe in detail the results from
Illustris-1-Dark for $w$, $c/a$ and $b/a$ for a fixed number of
satellites $N_s=11$.
The results from the other two simulations are included in the
Appendix \ref{appendix:plots}. 
The full covariance matrices are in the Appendix
\ref{appendix:matrices}.

\subsection{Physical Units}
%subsection{Plane Width}

Figure \ref{fig:physical_illustris1dark} summarizes the results in
physical units.
It compares three different groups: observations, simulations and the
observations randomized.
The left panel shows the results for M31 and the panel on the left for
the MW.

The most interesting outcome is that the MW plane width is smaller
than $\approx 98\%$ of the planes computed from the randomized distribution;
its  $c/a$ ratio is also significantly lower than the measured values for
the randomized distributions.   
On the other hand the results for $M31$ for the same quantities are
within $1-\sigma$ of the randomized results.

The comparison against observations also provides an extreme picture
for the MW. 
In this case the mean witdh from simulation is almost twice as the
mean width from the randomization. 
A possible criticism to this result is that the typical halo mass in
the simulation is larger than the it is for the MW. 
For this reason we renormalize all quantities ($w$, $c/a$ and $b/a$)
to the mean value and standard deviation provided by its spherical
randomization. 
In this way the physical scale of the halo becomes a second order
effect and only the deviations from asphericity are protagonist.

\subsection{Normalized Units}

Figure \ref{normalized_illustris1dark} summarizes  the results of
renormalizing to the randomized results.
The layout is the same as Figure \ref{physical_illustris1dark}.
Figure \ref{fig:scatter_width} summarizes the results for the width
measurements.
The left panel compares the results for the MW and M31
observations (stars) against its spherically randomized satellites
(circles).

@@

On the other hand the ratio for M31 is lower than the mean of the
spherical values but still well within its variance.
The middle panel in the same Figure shows the LG compared against the
results in the simulations. 
In this case we find a similar trend as before. 
The MW is atypical and M31 is within the variance from the simulation data.
This time, however, there are two MW-like halos out of the total
of 24 that show an $c/a$ as small as that of the MW.
The right panel shows the normalized results. 
The MW shows a low $c/a$ ratio between two and three
standard deviations away from the mean value of the spherical
distribution; this contrasts with the results for M31 which are close to
$1$ standard deviation away.

@@

\subsection{Multivariate Gaussian model}
